%%%%% DISCUSSION %%%%%%
\pagebreak

\section{Discussion}
% Summarize key findings of section results (\ref{sec:results}) in one or two paragraphs
% Interpretation of the results, discussion of the meaning in the context of motor learning
% Justify interpretation by citing the supporting key studies
% Discuss possible alternative interpretations of the data (if applicable)
% Mention limitations of my research 
    % Critique on framework: does not separate abstract from real tasks that are trained in the VE
    % Limitations of systematic review itself
    % Implications for future studies, mention practical implications

\paragraph{\nameref{sec:abstractspecific}}
This cluster contains one paper only, in which the vibrational feedback has a negative impact on motor learning. Even though the rhythmic task itself would probably benefit from haptic feedback (as has been shown by \cite{Graham2008} in a similar task), the vibrational feedback does not match with the intended action by the user, which is a unidirectional motion. Furthermore, as described by I. Lee et al, the vibration of the drumstick itself masked the vibrational feedback at higher frequencies, which made it harder for the participants to perceive the given feedback. Furthermore, the other types of feedback (e.g. FLOW, in which flowing bars across the screen showed when to hit the drum next) allowed for an anticipation of the next movement. This creates an uneven comparison with the vibrational feedback system. Therefore, the adverse effect on motor learning caused by poorly designed low-fidelity feedback, which is further disrupted by noise within the same modality, is unsurprising.

\paragraph{\nameref{sec:abstractbroad}}
The study conducted by Marchal-Crespo et al. used a self-built device with low haptic fidelity for haptic guidance. The task of bouncing a ball on a racket is classified as complex due to its nested redundancy: the number of execution variables exceeds the number of variables defining the task's outcome, both in execution (the joint configuration of the arm) and in the task itself (the positioning and speed of the racket when hitting the ball) \cite{Levac2019LearningReview}. Research on skill acquisition has shown how skill improvement is achieved by processing, and exploiting variability in movement \cite{Sternad2018ItsLearning}. Due to the constraints of the haptic device, however, the movement was limited to the sagittal plane only, which might have hampered motor learning. Furthermore, the participants might have become overreliant on haptic guidance as the frequency of bouncing the ball increased. The beneficial effect of the haptic guidance on bouncing the ball at low frequencies, which resembles discrete movements, can be explained by the lower difficulty of the task itself, not requiring exploitation of movement variability for motor learning.

\paragraph{\nameref{sec:abstractgeneric}}
The study by Hanashima et al. had several limitations that may explain the lack of observed differences in feedback modalities on learning accuracy. Firstly, tactile feedback was provided only on the waist and head, whereas learning the postures involved the entire body, including the arms and legs. Secondly, vibrotactile feedback may not be suitable for teaching postures as it lacks directional information, making it hard to adjust movements accurately. Additionally, the 200 Hz vibration frequency targeted the Pacinian corpuscles, which adapt quickly, thus reducing the participant's sensitivity to vibration \cite{Hanashima2023}. Lastly, the study did not isolate haptic feedback alone, as visual feedback was always present, complicating the assessment of haptic feedback's effectiveness.

In conclusion, low-fidelity feedback does not impact motor learning if it targets only a limited number of body parts involved in the task, lacks corrective information, and is designed in a way that reduces sensitivity.


\paragraph{\nameref{sec:representationalspecific}}
The positive impact of the haptic feedback system developed by Najdovski et al. on motor learning is unsurprising, as it provides haptic feedback that closely mimics the natural forces involved in tasks (e.g. forces experienced at the fingertips). Determining the stiffness of an object, which requires precise movements and online evaluation of tactile feedback, is facilitated by this system. The haptic feedback is delivered precisely where control of the object occurs, resulting in quicker transitions from feedback to reaction compared to translating visual cues into motion. This direct correspondence likely accounts for the faster evaluation of object stiffness and the higher accuracy in the experiments.


\paragraph{\nameref{sec:representationalbroad}}
The study by Chappell et al. demonstrates that mid-fidelity haptic feedback can enhance motor performance in a pick-and-place task compared to VR training without feedback. However, no significant improvement in skill transfer was observed when compared to a control group with no prior training. This outcome may be attributed to the small sample size (five participants per condition) and high inter-subject variability \cite{Chappell2022}. Additionally, discrepancies between the simulated and real hand limited the fidelity of the haptic feedback, potentially impacting the skill transfer results. Participants also reported high frustration levels with the haptic system, indicating a mismatch between expected and perceived stimuli and system-imposed constraints.

Gambaro et al. found that mid-fidelity feedback positively impacts motor learning when following a 2D trajectory. 
Similarly, Peña-Perez et al. noted that precise haptic feedback enhances tracking accuracy, as it is experienced when interacting with stiff virtual objects. However, interacting with softer objects, rendered with the same system, correlated with a worse motor performance. This effect may be explained by the fact that if we grasp a soft object, this also affects the perceived stimuli (e.g. a greater area of the fingers is covered, object deformation, etc.). This in turn may decrease the haptic fidelity of the system for the interaction with softer objects, which can negatively impact motor learning. The lack of vertical tactile feedback also potentially hindered accuracy in trajectory tracking.

In conclusion, mid-fidelity haptic feedback can positively influence motor learning by improving task performance and tracking accuracy. However, its effectiveness in skill transfer and overall accuracy can be limited by system constraints and the accuracy of the overall system.


\paragraph{\nameref{sec:representationalgeneric}}
The studies in this cluster can be divided into two groups: those using the HTC Vive controller (\cite{Vasudevan2020, Yang2023, McAnally2023}) and those utilizing wearable systems (\cite{LiuH2019, Trinitatova2023, Xia2023}).

The studies using the controller have in common that the vibrational feedback provided by the controller aligns well with the tasks. Vasudevan et al. and McAnally et al. conducted experiments with Fitts' tapping task, an abstract and discrete task, providing vibrational feedback upon tapping points. This enhances task performance, as the vibrational cues are sufficient for this simple task. The evaluation of these experiments also highlights a limitation of the haptic fidelity framework: due to the abstract nature of the task, there is no discrepancy between the experimental feedback and the natural occurrence of the task, resulting in a high haptic fidelity score, despite the feedback itself being abstract. Yang et al. examined the impact on motor learning using a drilling task, which naturally includes vibrational feedback. Overall, the tasks are well-designed and suit the vibrational feedback of the commercial controller.

The wearable systems are elaborate, featuring, for example, 40 vibration points on a vest \cite{Xia2023}, or a haptic glove with five vibration motors and a 3 DoF delta robot for haptic feedback in the palm \cite{Trinitatova2023}. These systems are well-designed to match the natural occurrence of tasks, such as grasping and lifting objects in VR with a glove-based system or telemanipulating a robot with hand movements. The tasks are much more complex, involving whole-body movements and 3D-trajectory following. As shown by Trinitatova et al. and Yang et al., the haptic feedback was able to reduce mental demand, potentially enabling participants to focus more on task execution.

In summary, mid-fidelity haptic feedback has a positive impact on motor learning, as it can reduce the mental load and improve task execution. However, the effectiveness of the feedback highly depends on the alignment with the task requirements. While simpler tasks benefit from vibrational feedback, more complex tasks require detailed and realistic feedback to enhance motor learning effectively.

\paragraph{\nameref{sec:realisticspecific}}
Four studies involve experiments with abstract tasks: rolling a ball along a beam \cite{Huang2006}, grabbing a virtual knob and pointing it to a marker \cite{Dai2023}, tracing a target line in 2D \cite{Fehlberg2012}, and exciting a spring-inertia system \cite{Huang2007}. When evaluating the haptic feedback fidelity of systems, the difference between natural haptic feedback and system-provided feedback is often considered. For abstract tasks, this congruence is perfect since there is no natural occurrence of the task, thereby increasing the system's haptic fidelity.

While using abstract tasks to evaluate the impact of haptic feedback on motor learning may be valuable for research, these studies have limited value in assessing whether a condition helps learn real-world tasks. This example also reveals a shortcoming in Muender et al.'s framework, as it does not distinguish between the nature of the task and whether the task in VR resembles a real-world task.

While Macuga et al. and Mohanty et al. concluded that congruent haptic feedback positively affects motor learning, they also demonstrated the detrimental effects of incongruent haptic feedback \cite{Macuga2019, Mohanty2023}. These findings highlight a shortcoming of the haptic feedback fidelity framework, as it does not account for the direction of feedback, which can adversely affect motor learning.

For the peg-in-hole task, Mohanty et al. reported that subjects relied on visual information for coarse object manipulations but needed kinesthetic perception for precise docking tasks. The disparity between the expected feedback (as seen on the display) and the provided feedback in this situation became especially salient and therefore may have led to the decrease in task performance. 
The human reliance on haptic feedback in fine manipulation tasks such as inserting a peg into a hole is logical, as some parts of the objects might be obscured by the objects themselves. This occlusion makes accurate object manipulation with visual feedback alone more challenging, thus increasing the reliance on haptic cues.

The study by Fehlberg et al. is particularly relevant for evaluating the impact of haptic feedback fidelity, as it included six conditions with haptic feedback, five of which fall into this cluster. Due to small differences in the location and type of haptic feedback provided, the data points are closely grouped. The greatest improvement in tracking the 2D trajectory was achieved with a virtual spring fixture on the active handrest, a condition with a medium-high fidelity score compared to the other conditions \cite{Fehlberg2012}. This performance increase may be explained by the fact that haptic guidance on the handrest via springs felt natural to the users while allowing for finer corrections with the fingers when using the Phantom Omni haptic device. The highest fidelity score in this cluster was achieved by the condition with the active handrest and virtual spring fixture on the Omni stylus, under which participants performed only slightly worse, with a similar mean completion time.

%%% REWRITE THIS %%%
In the study conducted by H. Lee et al., no significant long-term retention benefits from haptic feedback methods were found, as the effects did not extend beyond immediate post-training contexts. However, the retention task was quite trivial, using the same setup, which was neither very immersive nor challenging.
%%% REWRITE THIS %%%


To conclude, congruent haptic feedback significantly enhances motor learning, particularly in tasks requiring fine manipulation, while incongruent feedback (especially when pointing in the opposite direction) can be detrimental. 
\paragraph{\nameref{sec:realisticbroad}}

\paragraph{\nameref{sec:realisticgeneric}}



% Haptic feedback has been found to hinder motor learning, especially for tasks that naturally did not involve haptic feedback and when it was provided in a rather abstract way. Hanashima et al. for example provided vibrotactile feedback for posture learning and found the visual only condition to be superior over the visuo-tactile condition \cite{Hanashima2023}. However, when we learn a posture from another person in real life, we will also either depend on visual feedback only (for example when imitating the other person and using a mirror), or we will have actual guidance (for example from a physiotherapist). Vibrational feedback however does not seem to be a meaningful way to provide haptic feedback when learning postures.

% If the haptic rendering is amplified, but pointing in the same direction (for example when amplifying the errors, \cite{Oquendo2024}), this can be especially helpful for initially better skilled subjects. However, it is worse for subjects with initially less skill, as it might be overwhelming (according to challenge point theory). If the haptic feedback is incongruent, this is always worse for motor learning. For example, if the feedback is pointing in the opposite direction.

% \subsection{Shortcomings of framework}
% Framework mixes for haptic fidelity score multiple properties of the haptic devices and tries to accumulate these into one single score. This however does not cover the complexity of aspects that haptic devices have to offer. One example is the magnitude of feedback that is matched by the haptic device. This can either be explained by to which extent the haptic device can match the magnitude in real world, e.g. if the force in reality required 10N of force and the haptic device can render 10N of force. The other however is the force modality, as haptic devices can either render the natural forces of the object, but can also amplify the errors of the participant when doing a task, or have the forces point in the exact opposite direction. Even though this is only one in 8 evenly weighed foundational factors according to the framework \cite{Muender2022HapticReality}, it has a detrimental effect on motor learning. This is not appropriately taken into account in the framework.

\begin{comment}
Suggestions: For the post hoc evaluation of the haptic feedback fidelity, it would be helpful if researchers included specifications of the device used, such as hard- and software latency, maximum force, sensor and actuator accuracy, etc., even if the device is commercially available. This makes the objective rating of the feedback fidelity easier and quicker, as even for commercially used devices the specifications might not be available anymore at some point in the future.

Often, an artificial task is chosen, such as tracking a trajectory with a steering wheel, where the velocity of the car is constant to eliminate the use of foot pedals \cite{LeeH2014}. For the retention, the subjects are using the exact same setup, so parameters such as the degrees of freedom, and the stimuli of experiment and retention are the same, thus increasing the level of fidelity. However, the performance of the participants driving a real car, or even driving in a more realistic simulator is never evaluated, despite this actually being an interesting question. In the end, we want to know how we can effectively improve motor learning performance by providing haptic feedback to the user. If we are doing this only for artificial tasks, we are making the experimental setup easier and possibly cheaper, but not exploring the greater possibilities this technology might offer. 

One important finding is that haptic feedback might be especially important when learning a motor task that requires 3 dimensions. Studies that required the participants to follow a trajectory in 2D have often found no significant improvement in task performance when providing haptic feedback, compared to visual feedback only (\cite{Gambaro2014}, \cite{LiuG2014}, \cite{LeeH2014}), whereas studies involving trajectory following in 3 dimensions have shown a significant improvement with the introduction of haptic feedback (\cite{Grant2019}, \cite{Rodriguez2010}, ...)
    
\end{comment}


\begin{comment}
\onecolumn

\include{figures/tikz_graphic}

\begin{table}[]
\begin{tabular}{@{}p{0.13\textwidth}p{0.08\textwidth}p{0.23\textwidth}p{0.19\textwidth}p{0.27\textwidth}@{}}
\toprule
 Feedback Fidelity & Reference & Experimental Design & Feedback Type & Findings \\ \midrule
 Low & \cite{Huang2007} &  &  & Auditory cues with feed-forward control do not help with task performance \\ \\
 Mid & \cite{Morris2007} & Follow trajectory with stylus & Haptic device with the opposite of the embedded force pattern & Performance was worse in haptic only compared to visual only, and far worse than visuo-haptic condition \\ \\
 High & \cite{Huang2007} & Maximum excitement of dynamic system with rotary handle at resonance frequency &  & decreased variance, increased precision \\ \bottomrule
\end{tabular}
\end{table}

\twocolumn
\end{comment}